Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-11-18 Cost_manuscript.Rmd
adding more references

  Our findings provided partial support for our pre-registered hypotheses, which can be found in https://osf.io/2rsgm/registrations. In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points. This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [constantino; hayden; wikenheiser; sweiss]. This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [hayden; garrett; dundon]. In contrast, our prediction that effort requirements would produce more acceptances was only true for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment. These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [Eisenberger; Inzlicht], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; Olivola]. Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands. The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported this idea. However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.

  These choice dynamics ruled out a number of common explanatory candidates. For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic. The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that all our participants were high on need for cognition (i.e. Ceyda; Laura; Cacioppo et al 1996). Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates. We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting. Finally, the observed differences in acceptances between effort types cannot be explained by reward alone, as demands were rewarded at the same rate.

  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations. Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (Cognitive effort gained value by making trials feel shorter). Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2003], and are often experienced when we are fully immersed in a task [@czksdmsdkjdc]. The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks). These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios. ....This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman). Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.

  Our foraging paradigms allowed us to control for common shortfalls in the existing literature. For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving an outcome, investigations of the pursuit and receipt stages have been limited. Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [5,11,15,16,19]. However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the future [3,21,22; hayden, mobbs?]. Here we gave participants full knowledge of the available options, and provided an opportunity to actively experience the demands they accepted. Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time. This is often circumvented by comparing discounting functions and points at which individuals become indifferent to the increment in rewards []. Instead, we eliminated this possibility by fixating the handling time for all demands, which allowed us to probe people's preferences directly. In addition, the between-subjects experiment provided a baseline of foraging behavior, particularly in the traditional experimental case of foraging by waiting for the next reward []. This baseline helped us interpret the findings of the second experiment. Finally, the existence of optimal strategies let us know that people acted as if effort was attractive. This was evidenced by both the lower earnings by the cognitive effort group, and by the base OC model. Of note is that the optimality of the strategies produced by each cost depended on the richness of the block. This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.

>>>>

  Our findings provided partial support for our pre-registered hypotheses, which can be found in https://osf.io/2rsgm/registrations. In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points. This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013]. This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020]. In contrast, our prediction that effort requirements would produce more acceptances was only true for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment. These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; @Olivola2013]. Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands. The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported this idea. However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.

  These choice dynamics ruled out a number of common explanatory candidates. For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic. The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that all our participants were high on need for cognition [@Cacioppo1996; @Sayali2019]. Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates. We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweiss2018], as participants expressed their choices as early as possible, resulting in occassional underharvesting. Finally, the observed differences in acceptances between effort types cannot be explained by reward alone, as demands were rewarded at the same rate.

  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations. Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (Cognitive effort gained value by making trials feel shorter). Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2009], and are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014]. The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks). These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios. ....This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman). Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.

  Our foraging paradigms allowed us to control for common shortfalls in the existing literature. For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving an outcome, investigations of the pursuit and receipt stages have been limited. Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a]. However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the future [@Fawcett2012; @Frederick2002; @Sozou1998]. Here we gave participants full knowledge of the available options, and provided an opportunity to actively experience the demands they accepted. Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time. This is often circumvented by comparing discounting functions and points at which individuals become indifferent to the increment in rewards [@Massar2015; @Prevost2010]. Instead, we eliminated this possibility by fixating the handling time for all demands, which allowed us to probe people's preferences directly. In addition, the between-subjects experiment provided a baseline of foraging behavior, particularly in the traditional experimental case of foraging by waiting for the next reward []. This baseline helped us interpret the findings of the second experiment. Finally, the existence of optimal strategies let us know that people acted as if effort was attractive. This was evidenced by both the lower earnings by the cognitive effort group, and by the base OC model. Of note is that the optimality of the strategies produced by each cost depended on the richness of the block. This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
